### 2017-06-07 paper.tex
Getting latest version of template

@@

% enumerate package lets us use letters instead of numbers
\usepackage{enumerate}

@@

\usepackage{color}

@@

%% Include all macros below
\newcommand{\rulemajor}[1]{\section{#1}}
\begin{document}
\vspace*{0.2in}

\begin{flushleft}
{\Large
\textbf\newline{Ten Simple Rules for Collaborative Lesson Development}
}
\newline
\\
{Gabriel~A.~Devenyi}\textsuperscript{1},
{R\'{e}mi~Emonet}\textsuperscript{2},
{Rayna~M.~Harris}\textsuperscript{3},
{Kate~Hertweck}\textsuperscript{4},
{Damien~Irving}\textsuperscript{5},
{Ian~Milligan}\textsuperscript{6},
{Greg~Wilson}\textsuperscript{7, *}
\\
\textbf{1} Douglas Mental Health University Institute, McGill University / gdevenyi@gmail.com \\
\textbf{2} Universit\'{e} Jean Monnet / remi.emonet@univ-st-etienne.fr \\
\textbf{3} The University of Texas at Austin / rayna.harris@utexas.edu \\
\textbf{4} The University of Texas at Tyler / khertweck@uttyler.edu \\
\textbf{5} CSIRO Oceans and Atmosphere / irving.damien@gmail.com \\
\textbf{6} University of Waterloo / i2millig@uwaterloo.ca \\
\textbf{7} Rangle.io / gvwilson@third-bit.com
\\
* Corresponding author.
\end{flushleft}

\begin{abstract}

\noindent
Lessons take significant effort to build,
and even more effort to maintain.
The collaborative code development methods pioneered by the open source community
offer a way forward,
allowing us to create lessons which are open,
accessible,
and continually updated and improved by a community of contributors.
This paper provides ten simple rules that can help others create sustainable lessons.

\end{abstract}

\section*{Author Summary}

@@

@@

\rulemajor{Clarify your audience.}

@@

\rulemajor{Build community around lessons.}

@@

\rulemajor{Reduce, re-use, recycle.}

@@

\rulemajor{Build modular lessons that can be re-purposed.}

@@

\rulemajor{Encourage and empower contributors.}

@@

\rulemajor{Teach best practices for lesson development.}

@@

\rulemajor{Publish periodically and recognize contributions.}

@@

\rulemajor{Evaluate lessons at several scales.}

@@

\rulemajor{Link to other resources.}

@@

\rulemajor{You can't please everyone.}

@@

\bibliography{paper}

>>>>

% Template for PLoS
% Version 3.4 January 2017
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

@@

@@

@@

%% Include all macros below

% \newcommand{\lorem}{{\bf LOREM}}
% \newcommand{\ipsum}{{\bf IPSUM}}
\newcommand{\rulemajor}[1]{\section{#1}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules for collaborative lesson development} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
{Gabriel~A.~Devenyi}\textsuperscript{1{\ddag}},
{R\'{e}mi~Emonet}\textsuperscript{2{\ddag}},
{Rayna~M.~Harris}\textsuperscript{3{\ddag}},
{Kate~Hertweck}\textsuperscript{4{\ddag}},
{Damien~Irving}\textsuperscript{5{\ddag}},
{Ian~Milligan}\textsuperscript{6{\ddag}},
{Greg~Wilson}\textsuperscript{7{\ddag}*}
\\
\bigskip
\textbf{1} Douglas Mental Health University Institute, McGill University / gdevenyi@gmail.com \\
\textbf{2} Universit\'{e} Jean Monnet / remi.emonet@univ-st-etienne.fr \\
\textbf{3} The University of Texas at Austin / rayna.harris@utexas.edu \\
\textbf{4} The University of Texas at Tyler / khertweck@uttyler.edu \\
\textbf{5} CSIRO Oceans and Atmosphere / irving.damien@gmail.com \\
\textbf{6} University of Waterloo / i2millig@uwaterloo.ca \\
\textbf{7} Rangle.io / gvwilson@third-bit.com \\

\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
{\ddag} These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
% \ddag These authors also contributed equally to this work.

% Current address notes
% \textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Deceased author note
% \dag Deceased

% Group/Consortium Author Note
% \textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* corresponding author

\end{flushleft}

% Please keep the abstract below 300 words

\linenumbers

\section*{Abstract}

Lessons take significant effort to build,
and even more effort to maintain.
The collaborative code development methods pioneered by the open source community
offer a way forward,
allowing us to create lessons which are open,
accessible,
and continually updated and improved by a community of contributors.
This paper provides ten simple rules that can help others create sustainable lessons.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}

@@

% Use "Eq" instead of "Equation" for equation citations.

@@

\rulemajor{Clarify your audience}

@@

\rulemajor{Build community around lessons}

@@

\rulemajor{Reduce, re-use, recycle}

@@

\rulemajor{Build modular lessons that can be re-purposed}

@@

\rulemajor{Encourage and empower contributors}

@@

\rulemajor{Teach best practices for lesson development}

@@

\rulemajor{Publish periodically and recognize contributions}

@@

\rulemajor{Evaluate lessons at several scales}

@@

\rulemajor{Link to other resources}

@@

\rulemajor{You can't please everyone}

@@

\nolinenumbers

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
%

\begin{thebibliography}{1}

\bibitem{hlw}
Ambrose SA, Bridges MW, DiPietro M, Lovett MC, Norman MK.
\newblock How Learning Works.
\newblock Jossey-Bass; 2010.

\bibitem{wiggins-mctighe}
Wiggins G, McTighe J.
\newblock Understanding by Design.
\newblock 2nd ed. Association for Supervision and Curriculum Development; 2005.

\bibitem{lessons-learned}
Wilson G.
\newblock Software Carpentry: Lessons Learned.
\newblock F1000Research. 2016;3(62).
\newblock doi:{10.12688/f1000research.3-62.v2}.

\bibitem{choral-explanations}
Caulfield M. Choral Explanations; 2016.
\newblock https://hapgood.us/2016/05/13/choral-explanations/.

\bibitem{producing-oss}
Fogel K.
\newblock Producing Open Source Software.
\newblock O'Reilly; 2005.

\end{thebibliography}
